Preparing articles for submission to the \\ Archive of Numerical Software

### 2011-05-27 paper.tex
Some more work on style file(s)
git-svn-id: https://svn.mathsim.eu/documents/publications/journal/style@2712 a653633e-0a08-0410-9ecb-ed4064e9718a

\title{Preparing articles for submission to the\\
  Archive of Numerical Software}
\author[1]{Wolfgang Bangerth}
\author[2]{Peter Bastian}
\author[1]{Guido Kanschat\thanks{Additional thanks to my neighbor's dog
  for waking me up on time to work on this style file}}
\author[3]{Michael Heroux}
\author[4]{Anders Logg}
\affil[1]{Department of Mathematics, Texas A\&M University}
\affil[2]{IWR, Universit\"at Heidelberg}
\affil[3]{Sandia National Laboratories}
\affil[4]{Simula, Oslo}
\runningtitle{Preparing articles for ANS}
\runningauthor{Bangerth, Bastian, Kanschat, Heroux, Logg}

\begin{document}

@@

\begin{abstract}
  This document describes the general structure of the
  \texttt{ansarticle} document class and serves as an example for its
  usage. \texttt{ansarticle.cls} is based on the standard \LaTeX{}
  \texttt{article.cls} as well as a few other standard packages. It
  fixes most style parameters to the preferred style of the Archive of
  Numerical Software.
\end{abstract}

\section{Usage}

@@

\subsection{Requirements}

Upon loading, \texttt{ansarticle.cls} requires the following packages:

% TODO: Anders, please update!

\begin{itemize}
\item \texttt{times} and \texttt{mathptm} to use postscript fonts
\item \texttt{hyperref} in order to typeset hyper-links in the text
\item \texttt{fancyhdr} for page headers and footers
\item \texttt{authblk} for more convenient handling of author and
  affiliation lists
\item \texttt{listings} for source code listings
\end{itemize}
These packages are part of standard \TeX{} distributions and should
not cause any difficulties.

\subsection{Mathematical formul\ae}

We recommend using the \texttt{amsmath} package for setting
mathematical formul\ae{}, and we guarantee compatibility with the
\texttt{ansarticle} style.

% TODO: [GK] What about math fonts

\subsection{Supplementary material}
Additional material, chich is not part of the article text, but part
of the submission, for instance setup scripts or video output, can be
linked from the article, using the \texttt{hyperref} commands
(\texttt{hyperref} is automaticly included by
\texttt{ansarticle}). URLs to such material should start with the
filename. A suitable prefix will be added to the links in the
editorial process.

\subsection{Code samples}

@@

\subsubsection{C++}
code should be compliant with the current C++ standard. Two
commands are provided to prettyprint C++ code. First, an environment
to put C++ code into the LaTeX file, namely

@@

\section{Production after article was accepted}
\subsection{Publication metadata}

@@

\section{Philosophi\ae{} Naturalis Principia Mathematica}

Excerpt from~\cite{Newton87}.

@@

\subsubsection{Def. I}
Quantitas Materi\ae{} est mensura ejusdem orta ex illius Densitate \&
Magnitudine conjunctim.

>>>>

\title{Preparing articles for submission to the \\
       Archive of Numerical Software}
\author[1]{Wolfgang Bangerth}
\author[2]{Peter Bastian}
\author[1]{Guido Kanschat\thanks{Additional thanks to my neighbor's dog
  for waking me up on time to work on this style file}}
\author[3]{Michael Heroux}
\author[4]{Anders Logg}
\affil[1]{Department of Mathematics, Texas A\&M University}
\affil[2]{IWR, Universit\"at Heidelberg}
\affil[3]{Sandia National Laboratories}
\affil[4]{Simula Research Laboratory}
\runningtitle{Preparing articles for ANS}
\runningauthor{Bangerth, Bastian, Kanschat, Heroux, Logg}

%------------------------------------------------------------------------------
\begin{document}

@@

\begin{abstract}
  This document describes the general structure of the
  \texttt{ansarticle} document class and serves as an example for its
  usage. \texttt{ansarticle.cls} is based on the standard \LaTeX{}
  \texttt{article.cls} and a few other standard packages. It fixes
  style parameters to the preferred style of the Archive of Numerical
  Software (ANS).
\end{abstract}

%------------------------------------------------------------------------------
\section{Requirements}

To write an article for ANS, you need to download the following files
from the ANS web page:
\begin{itemize}
\item
  \emp{paper.tex}, the source file for this document and a template for
  authors;
\item
  \emp{ansarticle.cls}, the ANS document class file;
\item
  \emp{anslistings.sty}, the ANS style file for typesetting of code;
\item
  \emp{bibliography.bib}, a bibliography with some important
  references;
\item
  \emp{Makefile}, useful for building your document.
\end{itemize}

@@

Upon loading, \texttt{ansarticle.cls} requires the following packages:
\emp{a4wide},
\emp{anslistings},
\emp{algorithm},
\emp{algorithmicx},
\emp{amsmath},
\emp{amssymb},
\emp{booktabs},
\emp{fancyhdr},
\emp{graphicx},
\emp{hyperref},
\emp{authblk},
\emp{lastpage},
\emp{listings.}
These packages are part of standard \TeX{} distributions and should
not cause any difficulties.

%------------------------------------------------------------------------------
\section{Usage}

\subsection{Building the document}

Use this file (\emp{paper.tex}) as a template for your article. Then
simply type \emp{make} to build your article. This will call
\emp{pdflatex} to generate the PDF file \emp{paper.pdf}. To also call
\emp{bibtex}, type \emp{make final}.

\subsection{Typesetting mathematical formul\ae}

The ANS document class uses the amsmath and amssymb packages for
improved typesetting of mathematical formul\ae like, e.g., this one:
\begin{equation}
  \cfrac{1}{\sqrt{2}+
    \cfrac{1}{\sqrt{2}+
      \cfrac{1}{\sqrt{2}+\dotsb
  }}}.
\end{equation}

Make sure that you familiarize yourself with the \emp{amsmath}
environments \emp{multline}, \emp{align} and \emp{split} (and know the
differences between them). Avoid home-made splitting using
\emp{\{array\}\{rcl\}}.

\subsection{Typesetting tables}

\fixme{Write something about typesetting tables with \emp{booktabs}.}

\subsection{Typesetting code}

@@

\subsubsection{C++}

Code should be compliant with the current C++ standard. Two commands
are provided to prettyprint C++ code. First, an environment to put C++
code into the LaTeX file, namely

\fixme{Adjust width of code box, a little too wide now.}

@@

\subsection{Handling supplementary material}

Additional material, chich is not part of the article text, but part
of the submission, for instance setup scripts or video output, can be
linked from the article, using the \texttt{hyperref} commands
(\texttt{hyperref} is automaticly included by
\texttt{ansarticle}). URLs to such material should start with the
filename. A suitable prefix will be added to the links in the
editorial process.

%------------------------------------------------------------------------------
\section{Production after article was accepted}
\subsection{Publication metadata}

@@

%------------------------------------------------------------------------------
\section{Philosophi\ae{} Naturalis Principia Mathematica}

Excerpt from~\cite{Newton1687}.

@@

\subsubsection{Def. I}

Quantitas Materi\ae{} est mensura ejusdem orta ex illius Densitate \&
Magnitudine conjunctim.
